Figure 2 and figure 2 supplementary material

### 2022-03-15 Figures/Figure2.Rmd
Save corrplot Figure2.Rmd

```{r}
library(tidyverse)
library(Hmisc)
library(ggridges)
```

@@

    ct_corrplots[[ct]] <- add_row(store_corrs, order) %>% dplyr::mutate(measure2 = factor(measure2, levels = order$measure2)) %>% dplyr::arrange(factor(measure2, levels = order$measure2)) %>%
    ggplot(aes(measure2, measure1, fill=r, label=round(r_if_sig,2))) +
    geom_tile() +
      labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= ct, 
         subtitle="Only significant correlation coefficients shown (95% I.C.)") +
    scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1)) +
    geom_text() +
    theme_classic() +
    scale_x_discrete(expand=c(0,0)) +
    scale_y_discrete(expand=c(0,0)) +
    rotate_x_text(angle = 45)
   }
  return(ct_corrplots)
}

@@

```{r}
wrapper_corrplots(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA)
```

# Suplementary figure

```{r}
ridgeplots_by_cancer <- list()
tpurity_by_cancer <- list()
blank  <- ggplot() + theme_void()

>>>>

```{r}
library(tidyverse)
library(Hmisc)
library(ggridges)
library(ggtext)
library(glue)
```

@@

    ## Function to highlight the "average" row
    highlight = function(x, pat, color="black", family="") {
  ifelse(grepl(pat, x), glue("<b style='font-family:{family}; color:{color}'>{x}</b>"), x)
}

    ct_corrplots[[ct]] <- add_row(store_corrs, order) %>% dplyr::mutate(measure2 = factor(measure2, levels = order$measure2)) %>% dplyr::arrange(factor(measure2, levels = order$measure2)) %>%
    ggplot(aes(measure2, measure1, fill=r, label=round(r_if_sig,2))) +
    geom_tile() +
      labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= ct, 
         subtitle="Only significant correlation coefficients shown (95% I.C.)") +
    scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1)) +
    geom_text() +
    theme_classic() +
    scale_x_discrete(expand=c(0,0)) +
    scale_y_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red")) +
    rotate_x_text(angle = 45) + theme(axis.text.y=element_markdown())
   }
  return(ct_corrplots)
}

@@

```{r}
corrplots <- wrapper_corrplots(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA)
corrplots$Macrophages <- summary_corr$Macrophages + rremove("y.text")
corrplots$Neutrophils <- summary_corr$Neutrophils + rremove("y.text")
summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")

ggsave("Fig2_summary_corrplot.pdf", dpi = "print", width = 250, height = 100, units = "mm", scale = 2.5)
```

# Suplementary figure
```{r}
ridgeplots_by_cancer <- list()
tpurity_by_cancer <- list()
blank  <- ggplot() + theme_void()
